# Data transformation
## Crawling Datasets

All the dataset are crawled by the python. See the python scripts in folder "DataMinning" for the details of crawling datasets.

The price datasets: https://binance-docs.github.io/apidocs/spot/en/#change-log

The fundmental datasets: https://docs.glassnode.com/

The fear index: https://alternative.me/crypto/fear-and-greed-index/

We would used the Raw Datasets to create the target variables.

```{r}
library(tidyverse)
```


## Calcuate the basis:
Our trading strategy is based on the future swap and perpetual swap.
We will use the future swap and perpetual swap to calculate the basis ratio.

### Open BTC perpetual-swap datasets
Raw Data Set Description:

Time: the hour-level granularity time represent the time period between last hour to current hour \
Open: the first trade price in current time period \
High: the highest trade price in current time period \
Low: the lowest trade price in current time period \
Close: the last trade price in current time period \
Other features: Ignore
```{r}
df <- read.csv('./edav_onchaindata/BTC-USDT.csv')
head(df)
```
Calcuate the price by (high + low + close)/3, drop the useless columns
```{r}
df$price = (df$high + df$low +df$close)/3
df$date = as.Date(df$time)
btc_perp = df%>%
  group_by(date) %>%
  summarise_at(vars(price), list(name = mean))
names(btc_perp)[2] = "price"
head(btc_perp)
```

```{r}
Calculate_Basis <- function(perp,future,s) {
  future$price = (future$high + future$low +future$close)/3
  future$date = as.Date(future$time)
  future = future%>%
    group_by(date) %>%
    summarise_at(vars(price), list(name = mean))
  basis_df = merge(perp,future,by.x = "date", by.y= "date")
  names(basis_df)[2] <- 'perpetual'
  names(basis_df)[3] <- 'future'
  basis_df$basis <- (basis_df$future - basis_df$perpetual)/basis_df$perpetual * 100
  return (basis_df)
}
```

### Open btc future swap datasets 
There are 8 different future contracts. 6 are already expired, and 2 still exist in current market. The expiration date of those contracts are "2020-06-26", "2020-09-25", "2020-12-25", "2021-03-26", "2021-06-25", "2021-09-24", "2021-12-31", "2022-03-25" 

Raw Data Set Description:

Time: the hour-level granularity time represent the time period between last hour to current hour \
Open: the first trade price in current time period \
High: the highest trade price in current time period \
Low: the lowest trade price in current time period \
Close: the last trade price in current time period \
Other features: Ignore


### Calculate the % basis
Equation Basis  = (future - perpetual) / perpetual * 100 

```{r}
library(hash)
future_dir = './edav_onchaindata/future-swap'

names = list.files(future_dir)

futures <- hash()

for(name in names){
  future_path = paste(future_dir,name,sep='/')
  future <- read.csv(future_path)

  m = Calculate_Basis(btc_perp, future, name)
  last_row = nrow(m) - 2
  m <- m %>% slice( 3: last_row)
  futures[[substr(name, 10, 15)]] = m
}
```

Data Description

Date: the date \
Perpetual: the price of perpetual contract for a BTC \
Future: the price of future contract for a BTC \
Basis: the % ratio basis \

Example: the Basis DataFrame of the contract expired at 2020-06-26
```{r}
keys = keys(futures)
head(futures[[keys[1]]])
```

### Calculate Annual Basis:
Converting the quarter basis to the annual basis \

Annual Basis: because the basis highly depends on the expiration days. I will eliminate this trait by converting quarter basis to the annual basis.  \
Equation:    annual basis = quarter basis / days left * 365
```{r}
delivery_times = c("2020-06-26", "2020-09-25", "2020-12-25", "2021-03-26", 
                  "2021-06-25", "2021-09-24", "2021-12-31", "2022-03-25")

delivery_times = as.Date(delivery_times)
keys = keys(futures)

for (i in 1:8) {
  delivery_time = delivery_times[i]
  futures[[keys[i]]]$annual_basis <- (futures[[keys[i]]]$basis / as.numeric(delivery_time - futures[[keys[i]]]$date)) * 365
}

```

```{r}
head(futures[[keys[4]]])
```

## Fear Index

The crypto market behaviour is very emotional. People tend to get greedy when the market is rising. Also, people often sell their coins in irrational reaction of seeing red numbers. We assume the basis highly depend on emotion. When the market is extreme fear or extreme greedy, it might represents the basis is in the bottom or in the top.


```{r}
fear_index <- read.csv('./edav_onchaindata/fundamentalDf.csv')
fear_index$time = as.Date(fear_index$time)

head(fear_index)
```
```{r}
for (i in 1:8) {
  delivery_time = delivery_times[i]
  futures[[keys[i]]]$fear <- merge(futures[[keys[i]]],fear_index,by.x = "date", by.y= "time")$fear
}
```

```{r}
head(futures[[keys[1]]])
```
## Funding Rate

### Funding rate
Funding rates are periodic payments either to traders that are long or short based on the difference between perpetual contract markets and spot prices. Therefore, depending on open positions, traders will either pay or receive funding. 

Because Exchange only have funding rate data Set since 1/9/2021, we would not merge funding rate into basis dataframe

```{r}
funding_rate <- read.csv('./edav_onchaindata/Funding Rate History_BTCUSD Perpetual_2021-12-08.csv')
funding_rate$date = as.Date(funding_rate$ï..Time)
funding_rate$Funding.Rate = as.numeric(sub("%", "", funding_rate$Funding.Rate))

funding_rate = funding_rate%>%
  group_by(date) %>%
  summarise(Funding.Rate = sum(Funding.Rate))
write.csv(funding_rate,'./edav_onchaindata/Daily_Funding_Rate.csv', row.names = FALSE)
head(funding_rate)
```
## Daily Volatility

Volatility is a useful indicator to describe the degree of variation of a trading price series over time. We assume the higher Volatility, the higher possibility the basis reach bottom or top.

```{r}
df <- read.csv('./edav_onchaindata/BTC-USDT.csv')
df$date = as.Date(df$time)
df$price = (df$high + df$low +df$close)/3
df = df%>%
  group_by(date) %>%
  summarise(Volatility = sd(price))
head(df)
```
Merge Volatility into basis dataframe
```{r}
for (i in 1:8) {
  delivery_time = delivery_times[i]
  futures[[keys[i]]]$Volatility <- merge(futures[[keys[i]]],df, by.x = "date", by.y= "date")$Volatility
}

head(futures[[keys[1]]])
```


```{r}
for (i in 1:8) {
  delivery_time = delivery_times[i]
  write.csv(futures[[keys[i]]], paste("./edav_onchaindata/", keys[i], ".csv"), row.names = FALSE)
}
```




