# Results

We mainly explore basis trading from three different aspects: funding rate, basis, macro trend

## Funding Rate
We mainly explore funding rate by fear index and the number of consecutive days of fear(greed) market
```{r}
library(knitr)
library(ggplot2)  
library(png)  
path <- "./figures/Result/funding_histogram.png"
include_graphics(path)
```
### Fear Index vs Funding Rate

```{r}
path <- "./figures/Result/fear_funding.png"
include_graphics(path)
```
Clear linear relationship

### Consecutive extreme market days vs funding rate

####Consecutive Fear days vs funding rate
```{r}
path <- "./figures/Result/Consecutive_fear_funding.png"
include_graphics(path)
```
Not so obvious, but still can see longer days, lower funding rate

### Consecutive greed days vs funding rate

```{r}
path <- "./figures/Result/Consecutive_greed_funding.png"
include_graphics(path)
```

Not so obvious, but still can see longer days, larger funding rate


## Basis
The main idea of our trading strategy is to predict is the basis is on bottom or top. We explore basis from three different aspects: fear index, annual Basis and Volatility. 

### Fear index vs Basis
```{r}
path <- "./figures/Result/200626_exp.png"
include_graphics(path)
```

```{r}
path <- "./figures/Result/200925_exp.png"
include_graphics(path)
```

```{r}
path <- "./figures/Result/201225_exp.png"
include_graphics(path)
```


```{r}
path <- "./figures/Result/210326_exp.png"
include_graphics(path)
```

```{r}
path <- "./figures/Result/volatility_histogram.png"
include_graphics(path)
```
## Model:


### Run Model
Base on our model, we can tell you the right point to open the position (without info leaking)

```{r}
path <- "./figures/Result/strategy_decision_200626.png"
include_graphics(path)
```

```{r}
path <- "./figures/Result/strategy_decision_200925.png"
include_graphics(path)
```

```{r}
path <- "./figures/Result/strategy_decision_201225.png"
include_graphics(path)
```

```{r}
path <- "./figures/Result/strategy_decision_210326.png"
include_graphics(path)
```

```{r}
path <- "./figures/Result/strategy_decision_210924.png"
include_graphics(path)
```